### 2020-01-23 experiments.tex
projects

@@

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & \multicolumn{2}{|c|}{Findings} & \multicolumn{2}{|c|}{Mutation Score}  & Mutant \\
    Tool & Mean & Median & Mean & Median & Ratio\\
    \hline
    \hline
    SpotBugs & 0.26 & 0.00 & 0.30 & 0.07 & 1.132 \\
    \hline
    PMD & 0.48 & 0.00 & 0.09 & 0.00 & 0.183 \\
    \hline
    Infer & 0.00 & 0.00 & 0.00 & 0.00 &  0.006 \\
    \hline
  \end{tabular}
  \caption{Java tools: number of findings and mutation scores over all files.}
  \label{tab:scorejava}
\end{table}

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & & \multicolumn{2}{|c|}{} & \multicolumn{2}{|c}{Clean For All (1,185)} \\
    & \# Clean & \multicolumn{2}{|c|}{Mutation Score} &  \multicolumn{2}{|c}{Mutation Score}\\
    Tool & Files & Mean & Median & Mean & Median\\
    \hline
    \hline
    SpotBugs & 1,426 & 0.32 & 0.05 & 0.37 & 0.06 \\
    \hline
    PMD & 1,359 & 0.08 & 0.00 & 0.08 & 0.00 \\
    \hline
    Infer & 1,598 & 0.00 & 0.00 & 0.00 & 0.00 \\
    \hline
  \end{tabular}
  \caption{Java tools: clean file counts and mutation scores.}
  \label{tab:cleanjava}
\end{table}

@@

>>>>

70,825 mutants

@@

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & \multicolumn{2}{|c|}{Findings} & \multicolumn{2}{|c|}{Mutation Score}  & Mutant \\
    Tool & Mean & Median & Mean & Median & Ratio\\
    \hline
    \hline
    SpotBugs & 0.47 & 0.00 & 0.37 & 0.21 & 0.7847 \\
    \hline
    PMD & 1.27 & 0.00 & 0.07 & 0.07 & 0.0562 \\
    \hline
    Infer & 0.07 & 0.00 & 0.00 & 0.00 &  0.0002 \\
    \hline
  \end{tabular}
  \caption{Java tools: number of findings and mutation scores over all projects.}
  \label{tab:scorejava}
\end{table}

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & & \multicolumn{2}{|c|}{} & \multicolumn{2}{|c}{Clean For All (10)} \\
    & \# Clean & \multicolumn{2}{|c|}{Mutation Score} &  \multicolumn{2}{|c}{Mutation Score}\\
    Tool & Projects & Mean & Median & Mean & Median\\
    \hline
    \hline
    SpotBugs & 12 & 0.42 & 0.46 & 0.44 & 0.46 \\
    \hline
    PMD & 11 & 0.07 & 0.07 & 0.07 & 0.07 \\
    \hline
    Infer & 14 & 0.00 & 0.00 & 0.00 & 0.00 \\
    \hline
  \end{tabular}
  \caption{Java tools: clean project counts and mutation scores.}
  \label{tab:cleanjava}
\end{table}

@@

167,511 mutants
